\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{University of Queensland} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge Epistasis follow-up \\[0.3cm] \huge *** summary *** \\ \horrule{2pt} \\[0.5cm] \date{}

### 2015-02-19 investigation/docs/overview.tex
uopdate

\begin{figure}[H]
\centering
\includegraphics[height=3in]{empF.png}
\caption*{Figure | The F-statistic corresponding to $p=4.48^{-6}$ and df1=4, df2=842 from a $H_0$ table is 7.67. This figure shows the empirical (ranked) F-statistic corresponding to $n * 4.48^{-6}$. Where $n * 4.48^{-6} < 1$, the largest F-statistic taken.}
\end{figure}

@@

\begin{table}[ht]
\centering
\begin{tabular}{llllll}
  \hline
gene & probename & snp1 & snp2 & $\lambda$ & Type1 \\ 
  \hline
ADK & ILMN\_2358626 & rs2395095 & rs10824092 & 1.15 & 0.06 \\ 
ATP13A1 & ILMN\_2134224 & rs4284750 & rs873870 & 1.82 & 0.119 \\ 
C21ORF57 & ILMN\_1795836 & rs9978658 & rs11701361 & 1.43 & 0.085 \\ 
CSTB & ILMN\_1761797 & rs9979356 & rs3761385 & 1.05 & 0.053 \\ 
CTSC & ILMN\_2242463 & rs7930237 & rs556895 & 1.12 & 0.054 \\ 
FN3KRP & ILMN\_1652333 & rs898095 & rs9892064 & 1.34 & 0.075 \\ 
GAA & ILMN\_2410783 & rs11150847 & rs12602462 & 1.38 & 0.081 \\ 
HNRPH1 & ILMN\_2101920 & rs6894268 & rs4700810 & 1.47 & 0.091 \\ 
LAX1 & ILMN\_1769782 & rs1891432 & rs10900520 & 1.22 & 0.066 \\ 
MBLN1 & ILMN\_2313158 & rs11981513 & rs13069559 & 3.36 & 0.242 \\ 
MBLN1 & ILMN\_2313158 & rs16864367 & rs13079208 & 2.28 & 0.161 \\ 
MBLN1 & ILMN\_2313158 & rs2030926 & rs13069559 & 3.39 & 0.241 \\ 
MBLN1 & ILMN\_2313158 & rs218671 & rs13069559 & 3.36 & 0.242 \\ 
MBLN1 & ILMN\_2313158 & rs2614467 & rs13069559 & 3.37 & 0.242 \\ 
MBLN1 & ILMN\_2313158 & rs7710738 & rs13069559 & 3.38 & 0.243 \\ 
MBP & ILMN\_2398939 & rs8092433 & rs4890876 & 1.19 & 0.066 \\ 
NAPRT1 & ILMN\_1710752 & rs2123758 & rs3889129 & 2.14 & 0.155 \\ 
NCL & ILMN\_2121437 & rs7563453 & rs4973397 & 1.2 & 0.065 \\ 
PRMT2 & ILMN\_1675038 & rs2839372 & rs11701058 & 2.77 & 0.199 \\ 
SNORD14A & ILMN\_1799381 & rs2634462 & rs6486334 & 2.45 & 0.168 \\ 
TMEM149 & ILMN\_1786426 & rs807491 & rs7254601 & 2.69 & 0.194 \\ 
TMEM149 & ILMN\_1786426 & rs8106959 & rs1843357 & 5.79 & 0.396 \\ 
TMEM149 & ILMN\_1786426 & rs8106959 & rs2351458 & 5.77 & 0.395 \\ 
TMEM149 & ILMN\_1786426 & rs8106959 & rs6718480 & 5.82 & 0.397 \\ 
TMEM149 & ILMN\_1786426 & rs8106959 & rs6926382 & 5.75 & 0.396 \\ 
TMEM149 & ILMN\_1786426 & rs8106959 & rs914940 & 5.76 & 0.395 \\ 
TMEM149 & ILMN\_1786426 & rs8106959 & rs9509428 & 5.82 & 0.398 \\ 
VASP & ILMN\_1743646 & rs1264226 & rs2276470 & 1.37 & 0.08 \\ 
RPL13 & ILMN\_2413278 & rs352935 & rs2965817 & 1.11 & 0.058 \\ 
TRA2A & ILMN\_1731043 & rs7776572 & rs11770192 & 1.36 & 0.079 \\ 
   \hline
\end{tabular}
\caption*{The $\lambda$ and type 1 error rates for the 30 (bonferroni-correction) significant replicated pairs mentioned in Hemani \emph{et al}.}
\end{table}

>>>>

\begin{figure}[H]
\centering
\includegraphics[height=3in]{empF.png}
\caption*{Figure | The F-statistic corresponding to $p=4.48^{-6}$ and df1=4, df2=842 from a $H_0$ table is 7.67. This figure shows the empirical (ranked) F-statistic corresponding to $n * 4.48^{-6}$. Where $n * 4.48^{-6} < 1$, the largest F-statistic taken. There are 96 pairs where the corresponding F statistic is less than 7.67}
\end{figure}

@@

\begin{table}[ht]
\centering
\begin{tabular}{llllll}
  \hline
gene & probename & snp1 & snp2 & $\lambda$ & Type1 \\ 
  \hline
ADK & ILMN\_2358626 & rs2395095 & rs10824092 & 1.15 & 0.06 \\ 
ATP13A1 & ILMN\_2134224 & rs4284750 & rs873870 & 1.82 & 0.119 \\ 
C21ORF57 & ILMN\_1795836 & rs9978658 & rs11701361 & 1.43 & 0.085 \\ 
CSTB & ILMN\_1761797 & rs9979356 & rs3761385 & 1.05 & 0.053 \\ 
CTSC & ILMN\_2242463 & rs7930237 & rs556895 & 1.12 & 0.054 \\ 
FN3KRP & ILMN\_1652333 & rs898095 & rs9892064 & 1.34 & 0.075 \\ 
GAA & ILMN\_2410783 & rs11150847 & rs12602462 & 1.38 & 0.081 \\ 
HNRPH1 & ILMN\_2101920 & rs6894268 & rs4700810 & 1.47 & 0.091 \\ 
LAX1 & ILMN\_1769782 & rs1891432 & rs10900520 & 1.22 & 0.066 \\ 
MBLN1 & ILMN\_2313158 & rs11981513 & rs13069559 & 3.36 & 0.242 \\ 
MBLN1 & ILMN\_2313158 & rs16864367 & rs13079208 & 2.28 & 0.161 \\ 
MBLN1 & ILMN\_2313158 & rs2030926 & rs13069559 & 3.39 & 0.241 \\ 
MBLN1 & ILMN\_2313158 & rs218671 & rs13069559 & 3.36 & 0.242 \\ 
MBLN1 & ILMN\_2313158 & rs2614467 & rs13069559 & 3.37 & 0.242 \\ 
MBLN1 & ILMN\_2313158 & rs7710738 & rs13069559 & 3.38 & 0.243 \\ 
MBP & ILMN\_2398939 & rs8092433 & rs4890876 & 1.19 & 0.066 \\ 
NAPRT1 & ILMN\_1710752 & rs2123758 & rs3889129 & 2.14 & 0.155 \\ 
NCL & ILMN\_2121437 & rs7563453 & rs4973397 & 1.2 & 0.065 \\ 
PRMT2 & ILMN\_1675038 & rs2839372 & rs11701058 & 2.77 & 0.199 \\ 
SNORD14A & ILMN\_1799381 & rs2634462 & rs6486334 & 2.45 & 0.168 \\ 
TMEM149 & ILMN\_1786426 & rs807491 & rs7254601 & 2.69 & 0.194 \\ 
TMEM149 & ILMN\_1786426 & rs8106959 & rs1843357 & 5.79 & 0.396 \\ 
TMEM149 & ILMN\_1786426 & rs8106959 & rs2351458 & 5.77 & 0.395 \\ 
TMEM149 & ILMN\_1786426 & rs8106959 & rs6718480 & 5.82 & 0.397 \\ 
TMEM149 & ILMN\_1786426 & rs8106959 & rs6926382 & 5.75 & 0.396 \\ 
TMEM149 & ILMN\_1786426 & rs8106959 & rs914940 & 5.76 & 0.395 \\ 
TMEM149 & ILMN\_1786426 & rs8106959 & rs9509428 & 5.82 & 0.398 \\ 
VASP & ILMN\_1743646 & rs1264226 & rs2276470 & 1.37 & 0.08 \\ 
RPL13 & ILMN\_2413278 & rs352935 & rs2965817 & 1.11 & 0.058 \\ 
TRA2A & ILMN\_1731043 & rs7776572 & rs11770192 & 1.36 & 0.079 \\ 
   \hline
\end{tabular}
\caption*{The $\lambda$ and type 1 error rates for the 30 (Bonferroni-correction) significant replicated pairs mentioned in Hemani \emph{et al}.}
\end{table}
